---
title: "Amy Shaw Dissertation Code Script"
output: html_notebook
---

## Script setup

Load packages used in analysis

```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(patchwork)
library(data.table)
library(scales)
```

Define plotting theme for figures

```{r}
theme_fancy <- function() {
  theme_bw() +
    theme(
      text = element_text(family = "Helvetica"),
      axis.text = element_text(size = 8, color = "black"),
      axis.title = element_text(size = 10, color = "black"),
      axis.line.x = element_line(size = 0.3, color = "black"),
      axis.line.y = element_line(size = 0.3, color = "black"),
      axis.ticks = element_line(size = 0.3, color = "black"),
      panel.border = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank(),
      panel.grid.minor.y = element_blank(),
      panel.grid.major.y = element_blank(),
      plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), units = , "cm"),
      plot.title = element_text(
        size = 10,
        vjust = 1,
        hjust = 0.5,
        color = "black"
      ),
      legend.text = element_text(size = 9, color = "black"),
      legend.title = element_text(size = 9, color = "black"),
      legend.position = c(0.9, 0.9),
      legend.key.size = unit(0.7, "line"),
      legend.background = element_rect(
        color = "black",
        fill = "transparent",
        size = 2,
        linetype = "blank"
      )
    )
}
```

## Lamu Data importing and processing

In this section 11 csv files from the Global Mangrove Watch 3.0 dataset are imported and processed. Clips were made in QGIS for Lamu County for the available observation years of 1996, 2007-2010 and 2015-2020.

The following processing steps are then take for each imported dataframe.

1.  Rename the column labelled with the observation year to 'Mangroves'. This column contains mangrove coverage in square meters for the QGIS pixel in question.
2.  Create a column called 'year' and set the value to the observation year.
3.  Drop columns that are not required retaining the 'Mangroves' and 'year' columns.

### Lamu County mangrove cover data import and initial processing

Import Lamu County 1996 mangrove data.

```{r}
Lamu1996Data <- read_csv("Data/Lamu1996Data.csv")
Lamu1996Data
```

Rename 1996 column to Mangroves.

```{r}
names(Lamu1996Data)[names(Lamu1996Data) == '1996'] <- 'Mangroves'
Lamu1996Data
```

Create year column and set the value to 1996.

```{r}
Lamu1996Data <- cbind(Lamu1996Data, year="1996")
Lamu1996Data
```

Drop columns PXLVAL and clipped1996data as neither is needed.

```{r}
Lamu1996Data = subset(Lamu1996Data,select = -c(PXLVAL, clipped1996data))
Lamu1996Data
```

Import Lamu County 2007 mangrove data.

```{r}
Lamu2007Data <- read_csv("Data/Lamu2007Data.csv")
Lamu2007Data
```

Rename 2007 column to Mangroves.

```{r}
names(Lamu2007Data)[names(Lamu2007Data) == '2007'] <- 'Mangroves'
Lamu2007Data
```

Create year column and set the value to 2007.

```{r}
Lamu2007Data <- cbind(Lamu2007Data, year="2007")
Lamu2007Data
```

Drop columns PXLVAL and clipped2007data as neither is needed.

```{r}
Lamu2007Data = subset(Lamu2007Data,select = -c(PXLVAL, clipped2007data))
Lamu2007Data
```

Import Lamu County 2008 mangrove data.

```{r}
Lamu2008Data <- read_csv("Data/Lamu2008Data.csv")
Lamu2008Data
```

Rename 2008 column to Mangroves.

```{r}
names(Lamu2008Data)[names(Lamu2008Data) == '2008'] <- 'Mangroves'
Lamu2008Data
```

Create year column and set the value to 2008.

```{r}
Lamu2008Data <- cbind(Lamu2008Data, year="2008")
Lamu2008Data
```

Drop columns PXLVAL and clipped2008data as neither is needed.

```{r}
Lamu2008Data = subset(Lamu2008Data,select = -c(PXLVAL, clipped2008data))
Lamu2008Data
```

Import Lamu County 2009 mangrove data.

```{r}
Lamu2009Data <- read_csv("Data/Lamu2009Data.csv")
Lamu2009Data
```

Rename 2009 column to Mangroves.

```{r}
names(Lamu2009Data)[names(Lamu2009Data) == '2009'] <- 'Mangroves'
Lamu2009Data
```

Create year column and set the value to 2009.

```{r}
Lamu2009Data <- cbind(Lamu2009Data, year="2009")
Lamu2009Data
```

Drop columns PXLVAL and clipped2009data as neither is needed.

```{r}
Lamu2009Data = subset(Lamu2009Data,select = -c(PXLVAL, clipped2009data))
Lamu2009Data
```

Import Lamu County 2010 mangrove data.

```{r}
Lamu2010Data <- read_csv("Data/Lamu2010Data.csv")
Lamu2010Data
```

Rename 2010 column to Mangroves.

```{r}
names(Lamu2010Data)[names(Lamu2010Data) == '2010'] <- 'Mangroves'
Lamu2010Data
```

Create year column and set the value to 2010.

```{r}
Lamu2010Data <- cbind(Lamu2010Data, year="2010")
Lamu2010Data
```

Drop columns PXLVAL and clipped2010data as neither is needed.

```{r}
Lamu2010Data = subset(Lamu2010Data,select = -c(PXLVAL, clipped2010data))
Lamu2010Data
```

Import Lamu County 2015 mangrove data.

```{r}
Lamu2015Data <- read_csv("Data/Lamu2015Data.csv")
Lamu2015Data
```

Rename 2015 column to Mangroves.

```{r}
names(Lamu2015Data)[names(Lamu2015Data) == '2015'] <- 'Mangroves'
Lamu2015Data
```

Create year column and set the value to 2015.

```{r}
Lamu2015Data <- cbind(Lamu2015Data, year="2015")
Lamu2015Data
```

Drop columns PXLVAL and clipped2015data as neither is needed.

```{r}
Lamu2015Data = subset(Lamu2015Data,select = -c(PXLVAL, clipped2015data))
Lamu2015Data
```

Import Lamu County 2016 Mangrove Data.

```{r}
Lamu2016Data <- read_csv("Data/Lamu2016Data.csv")
Lamu2016Data
```

Rename 2016 column to Mangroves.

```{r}
names(Lamu2016Data)[names(Lamu2016Data) == '2016'] <- 'Mangroves'
Lamu2016Data
```

Create year column and set the value to 2016.

```{r}
Lamu2016Data <- cbind(Lamu2016Data, year="2016")
Lamu2016Data
```

Drop columns PXLVAL and clipped2016data as neither is needed.

```{r}
Lamu2016Data = subset(Lamu2016Data,select = -c(PXLVAL, clipped2016data))
Lamu2016Data
```

Import Lamu County 2017 mangrove data.

```{r}
Lamu2017Data <- read_csv("Data/Lamu2017Data.csv")
Lamu2017Data
```

Rename 2017 column to Mangroves.

```{r}
names(Lamu2017Data)[names(Lamu2017Data) == '2017'] <- 'Mangroves'
Lamu2017Data
```

Create year column and set the value to 2017.

```{r}
Lamu2017Data <- cbind(Lamu2017Data, year="2017")
Lamu2017Data
```

Drop columns PXLVAL and clipped2017data as neither is needed.

```{r}
Lamu2017Data = subset(Lamu2017Data,select = -c(PXLVAL, clipped2017data))
Lamu2017Data
```

Import Lamu County 2018 mangrove data.

```{r}
Lamu2018Data <- read_csv("Data/Lamu2018Data.csv")
Lamu2018Data
```

Rename 2018 column to Mangroves.

```{r}
names(Lamu2018Data)[names(Lamu2018Data) == '2018'] <- 'Mangroves'
Lamu2018Data
```

Create year column and set the value to 2018.

```{r}
Lamu2018Data <- cbind(Lamu2018Data, year="2018")
Lamu2018Data
```

Drop PXLVAL column as it is not needed.

```{r}
Lamu2018Data = subset(Lamu2018Data,select = -c(PXLVAL))
Lamu2018Data
```

Import Lamu County 2019 mangrove data.

```{r}
Lamu2019Data <- read_csv("Data/Lamu2019Data.csv")
Lamu2019Data
```

Rename 2019 column to Mangroves.

```{r}
names(Lamu2019Data)[names(Lamu2019Data) == '2019'] <- 'Mangroves'
Lamu2019Data
```

Create year column and set the value to 2019.

```{r}
Lamu2019Data <- cbind(Lamu2019Data, year="2019")
Lamu2019Data
```

Drop columns PXLVAL and clipped2019data as neither is needed.

```{r}
Lamu2019Data = subset(Lamu2019Data,select = -c(PXLVAL, clipped2019data))
Lamu2019Data
```

Import Lamu County 2020 mangrove data.

```{r}
Lamu2020Data <- read_csv("Data/Lamu2020Data.csv")
Lamu2020Data
```

Rename 2020 column to Mangroves.

```{r}
names(Lamu2020Data)[names(Lamu2020Data) == '2020'] <- 'Mangroves'
Lamu2020Data
```

Create year column and set the value to 2020.

```{r}
Lamu2020Data <- cbind(Lamu2020Data, year="2020")
Lamu2020Data
```

Drop columns PXLVAL and clipped2020data as neither is needed.

```{r}
Lamu2020Data = subset(Lamu2020Data,select = -c(PXLVAL, clipped2020data))
Lamu2020Data
```

## Lamu County data merging, aggregation and further processing

The Lamu County data for each observation year is merged into a single data frame. The data is then aggregated to return the total Mangrove coverage in each year and converted into a new data frame. Next, the Total_Mangroves_Hectares column is created, which converts the Mangrove coverage figures from square metres to hectares. Lastly, the Total_Mangroves column, measured in square metres is dropped.

Merge all Lamu County Mangrove dataframes

```{r}
df1 <- bind_rows(Lamu1996Data, Lamu2007Data, Lamu2008Data, Lamu2009Data, Lamu2010Data, Lamu2015Data, Lamu2016Data, Lamu2017Data, Lamu2018Data, Lamu2019Data, Lamu2020Data)
df1
```

Check unique values to make sure all observation years are present.

```{r}
unique(df1$year)
```

Aggregate the data to return the total mangrove coverage in square metres by year.

```{r}
agg_tbl1 <- df1 %>% group_by(year) %>% summarise(Total_Mangroves=sum(Mangroves),.groups = 'drop')
agg_tbl1
```

Convert aggregated data into a new data frame.

```{r}
df2 <- agg_tbl1 %>% as.data.frame()
df2
```

Create Total_Mangroves_Hectares column, which converts the mangrove coverage from square metres to hectares.

```{r}
df2$Total_Mangroves_Hectares <- df2$Total_Mangroves / 10000
df2
```

Drop Total_Mangroves (sq metres) column as unnecessary.

```{r}
df2 = subset(df2,select = -c(Total_Mangroves))
df2
```

Duplicate data frame.

```{r}
df3 <- df2
df3
```

## MICP Data importing and processing

In this section 11 csv files from the Global Mangrove Watch 3.0 dataset are imported and processed. Clips were made in QGIS for the Manda Island Conservation Project (MICP) for the available observation years of 1996, 2007-2010 and 2015-2020.

The following processing steps are then take for each imported data frame.

1.  Rename the column labelled with the observation year to 'Mangroves'. This column contains mangrove coverage in square metres for the QGIS pixel in question.
2.  Create a column called 'year' and set the value to the observation year.
3.  Drop columns that are not required retaining the 'Mangroves' and 'year' columns.

#### MICP mangrove cover data import and initial processing

Import MICP 1996 Mangrove data.

```{r}
MICP1996Data <- read_csv("Data/MICP1996Data.csv")
MICP1996Data
```

Rename 1996 column to Mangroves.

```{r}
names(MICP1996Data)[names(MICP1996Data) == '1996area'] <- 'Mangroves'
MICP1996Data
```

Create year column and set the value to 1996.

```{r}
MICP1996Data <- cbind(MICP1996Data, year="1996")
MICP1996Data
```

Drop columns PXLVAL and clipped1996data as neither is needed.

```{r}
MICP1996Data = subset(MICP1996Data,select = -c(PXLVAL, clipped1996data))
MICP1996Data
```

Import MICP 2007 mangrove data.

```{r}
MICP2007Data <- read_csv("Data/MICP2007Data.csv")
MICP2007Data
```

Rename 2007 column to Mangroves.

```{r}
names(MICP2007Data)[names(MICP2007Data) == '2007'] <- 'Mangroves'
MICP2007Data
```

Create year column and set the value to 2007.

```{r}
MICP2007Data <- cbind(MICP2007Data, year="2007")
MICP2007Data
```

Drop columns PXLVAL and clipped2007data as neither is needed.

```{r}
MICP2007Data = subset(MICP2007Data,select = -c(PXLVAL, clipped2007data))
MICP2007Data
```

Import MICP 2008 Mangrove data.

```{r}
MICP2008Data <- read_csv("Data/MICP2008Data.csv")
MICP2008Data
```

Rename 2008 column to Mangroves.

```{r}
names(MICP2008Data)[names(MICP2008Data) == '2008'] <- 'Mangroves'
MICP2008Data
```

Create year column and set the value to 2008.

```{r}
MICP2008Data <- cbind(MICP2008Data, year="2008")
MICP2008Data
```

Drop columns PXLVAL and clipped2008data as neither is needed.

```{r}
MICP2008Data = subset(MICP2008Data,select = -c(PXLVAL, clipped2008data))
MICP2008Data
```

Import MICP 2009 mangrove data.

```{r}
MICP2009Data <- read_csv("Data/MICP2009Data.csv")
MICP2009Data
```

Rename 2009 column to Mangroves.

```{r}
names(MICP2009Data)[names(MICP2009Data) == '2009'] <- 'Mangroves'
MICP2009Data
```

Create year column and set the value to 2009.

```{r}
MICP2009Data <- cbind(MICP2009Data, year="2009")
MICP2009Data
```

Drop columns PXLVAL and clipped2009data as neither is needed.

```{r}
MICP2009Data = subset(MICP2009Data,select = -c(PXLVAL, clipped2009data))
MICP2009Data
```

Import MICP 2010 mangrove data.

```{r}
MICP2010Data <- read_csv("Data/MICP2010Data.csv")
MICP2010Data
```

Rename 2010 column to Mangroves.

```{r}
names(MICP2010Data)[names(MICP2010Data) == '2010'] <- 'Mangroves'
MICP2010Data
```

Create year column and set the value to 2010.

```{r}
MICP2010Data <- cbind(MICP2010Data, year="2010")
MICP2010Data
```

Drop columns PXLVAL and clipped2010data as neither is needed.

```{r}
MICP2010Data = subset(MICP2010Data,select = -c(PXLVAL, clipped2010data))
MICP2010Data
```

Import MICP 2015 mangrove data.

```{r}
MICP2015Data <- read_csv("Data/MICP2015Data.csv")
MICP2015Data
```

Rename 2015 column to Mangroves.

```{r}
names(MICP2015Data)[names(MICP2015Data) == '2015'] <- 'Mangroves'
MICP2015Data
```

Create year column and set the value to 2015.

```{r}
MICP2015Data <- cbind(MICP2015Data, year="2015")
MICP2015Data
```

Drop columns PXLVAL and clipped2015data as neither is needed.

```{r}
MICP2015Data = subset(MICP2015Data,select = -c(PXLVAL, clipped2015data))
MICP2015Data
```

Import MICP 2016 mangrove data.

```{r}
MICP2016Data <- read_csv("Data/MICP2016Data.csv")
MICP2016Data
```

Rename 2016 column to Mangroves.

```{r}
names(MICP2016Data)[names(MICP2016Data) == '2016'] <- 'Mangroves'
MICP2016Data
```

Create year column and set the value to 2016.

```{r}
MICP2016Data <- cbind(MICP2016Data, year="2016")
MICP2016Data
```

Drop columns PXLVAL and clipped2016data as neither is needed.

```{r}
MICP2016Data = subset(MICP2016Data,select = -c(PXLVAL, clipped2016data))
MICP2016Data
```

Import MICP 2017 mangrove data.

```{r}
MICP2017Data <- read_csv("Data/MICP2017Data.csv")
MICP2017Data
```

Rename 2017 column to Mangroves.

```{r}
names(MICP2017Data)[names(MICP2017Data) == '2017'] <- 'Mangroves'
MICP2017Data
```

Create year column and set the value to 2017.

```{r}
MICP2017Data <- cbind(MICP2017Data, year="2017")
MICP2017Data
```

Drop columns PXLVAL and clipped2017data as neither is needed.

```{r}
MICP2017Data = subset(MICP2017Data,select = -c(PXLVAL, clipped2017data))
MICP2017Data
```

Import MICP 2018 mangrove data.

```{r}
MICP2018Data <- read_csv("Data/MICP2018Data.csv")
MICP2018Data
```

Create year column and set the value to 2018.

```{r}
names(MICP2018Data)[names(MICP2018Data) == '2018area'] <- 'Mangroves'
MICP2018Data
```

Create a 2018 year column

```{r}
MICP2018Data <- cbind(MICP2018Data, year="2018")
MICP2018Data
```

Drop PXLVAL column as it is not needed.

```{r}
MICP2018Data = subset(MICP2018Data,select = -c(PXLVAL))
MICP2018Data
```

Import MICP 2019 mangrove data.

```{r}
MICP2019Data <- read_csv("Data/MICP2019Data.csv")
MICP2019Data
```

Rename 2019 column to Mangroves.

```{r}
names(MICP2019Data)[names(MICP2019Data) == '2019'] <- 'Mangroves'
MICP2019Data
```

Create year column and set the value to 2019.

```{r}
MICP2019Data <- cbind(MICP2019Data, year="2019")
MICP2019Data
```

Drop columns PXLVAL and clipped2019data as neither is needed.

```{r}
MICP2019Data = subset(MICP2019Data,select = -c(PXLVAL, clipped2019data))
MICP2019Data
```

Import MICP 2020 mangrove data

```{r}
MICP2020Data <- read_csv("Data/MICP2020Data.csv")
MICP2020Data
```

Rename 2020 column to Mangroves.

```{r}
names(MICP2020Data)[names(MICP2020Data) == '2020'] <- 'Mangroves'
MICP2020Data
```

Create year column and set the value to 2020.

```{r}
MICP2020Data <- cbind(MICP2020Data, year="2020")
MICP2020Data
```

Drop columns PXLVAL and clipped2020data as neither is needed

```{r}
MICP2020Data = subset(MICP2020Data,select = -c(PXLVAL, clipped2020data))
MICP2020Data
```

## MICP data merging, aggregation and further processing

The MICP data for each observation year is merged into a single dataframe. The data is then aggregated to return the total Mangrove coverage in each year. Next, the Total_Mangroves_Hectares column is created, which converts the Mangrove coverage figures from square metres to hectares. Lastly, the Total_Mangroves column, measured in square metres is dropped.

Merge all MICP mangrove datasets by year

```{r}
df4 <- bind_rows(MICP1996Data, MICP2007Data, MICP2008Data, MICP2009Data, MICP2010Data, MICP2015Data, MICP2016Data, MICP2017Data, MICP2018Data, MICP2019Data, MICP2020Data)
df4
```

Check unique values to make sure all observation years are present.

```{r}
unique(df4$year)
```

Aggregate the data to return the total mangrove coverage in square metres by year.

```{r}
agg_tbl <- df4 %>% group_by(year) %>% summarise(Total_Mangroves=sum(Mangroves),.groups = 'drop')
agg_tbl
```

Convert aggregated data into a new data frame

```{r}
df5 <- agg_tbl %>% as.data.frame()
df5
```

Create Total_Mangroves_Hectares column, which converts the mangrove coverage from square metres to hectares.

```{r}
df5$Total_Mangroves_Hectares <- df5$Total_Mangroves / 10000
df5
```

Drop Total_Mangroves (sq metres) columns as unnecessary.

```{r}
df5 = subset(df5,select = -c(Total_Mangroves))
df5
```

Duplicate data frame.

```{r}
df6 <- df5
df6
```


## Percentage change analysis

### MICP percentage change calculation

Convert MICP data into a data.table

```{r}
setDT(df6)
class(df6)
```


Calculate the year-on-year relative change for MICP data. The change column represents the relative change from the previous year's value for Total_Mangrove_Hectares.

```{r}
df6[ , change := (Total_Mangroves_Hectares - shift(Total_Mangroves_Hectares)) / shift(Total_Mangroves_Hectares)]  
df6
```

Calculate the year-on-year percentage change and return in the column percentchange

```{r}
df6$percentchange <- percent(df6$change, accuracy=.1)
df6
```

Convert the output from a data table to a data frame

```{r}
df7 <- as.data.frame(df6) 
df7
```

Create a location column and set the value to 'MICP'

```{r}
df7 <- cbind(df7, location="MICP")
df7
```

### Lamu percentage change calculation

Convert Lamu data into a data.table

```{r}
setDT(df3)
class(df3)
```

Calculate the year-on-year relative change for Lamu data. The change column represents the relative change from the previous year's value for Total_Mangrove_Hectares.

```{r}
df3[ , change := (Total_Mangroves_Hectares - shift(Total_Mangroves_Hectares)) / shift(Total_Mangroves_Hectares)]  
df3
```

Calculate the year-on-year percentage change and return in the column percentchange

```{r}
df3$percentchange <- percent(df3$change, accuracy=.1)
df3
```

Convert the output from a data table to a data frame

```{r}
df8 <- as.data.frame(df3) 
df8
```

Create a location column and set the value to 'Lamu County'

```{r}
df8 <- cbind(df8, location="Lamu County")
df8
```

### Percentage change visualisation

Merge Lamu and MICP dataframes

```{r}
df9 <- bind_rows(df8, df7)
df9
```

Check unique years to make sure all years are retained.

```{r}
unique(df9$year)
```

Filter out 1996 because there is not a previous year to compare it to.

```{r}
df9 <- na.omit(df9)
df9
```

Convert year column to numeric

```{r}
df9$year = as.numeric(as.character(df9$year)) 
df9
```

Create a line graph showing the year-on-year percentage change in mangrove cover for both MICP and Lamu County. The graph highlights the differences between MICP and Lamu County.

```{r}
fig1 <- ggplot(data=df9, aes(x=year, y=percentchange, group=location,
                           colour=location)) +
  geom_line() +
  geom_point() +
  theme_fancy() +
  theme(legend.position="right") +
  ggtitle("Lamu County and MICP annual percentage change in mangrove cover", ) +
  theme(plot.title = element_text(face="bold")) +
  xlab("Year") +
  ylab("Mangrove coverage change") +
  labs(color='Location') +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 11))

fig1

```

Save the graph into the plots folder

```{r}
filename = "Lamu County and MICP annual percentage change in mangrove cover"

ggsave(
  fig1,
  filename = paste0("Plots/", filename, ".png"),
  width = 23,
  height = 17,
  units = "cm"
)

ggsave(
  fig1,
  filename = paste0("Plots/", filename, ".pdf"),
  width = 23,
  height = 17,
  units = "cm"
)
```

## Absolute change visualisation

Create scatterplots and bar charts to visualise the absolute change in mangrove cover in the MICP and Lamu County.

Y axis scaler set to 3%

```{r}
y_axis_scaler <- 0.03
y_axis_scaler
```

Summarise MICP data

```{r}
summary(df7)
```

Calculate MICP data min and max values and store as a vector

```{r}
manda_range <- range(df7$Total_Mangroves_Hectares)
manda_range
```

Define the MICP line graph Y axis limit as 3% above the MICP data Max value.

```{r}
manda_y_axis_max <- manda_range[2] * (1+y_axis_scaler)
manda_y_axis_max
```

Define the MICP line graph Y axis limit as 3% below the MICP data Min value.

```{r}
manda_y_axis_min <- manda_range[1] * (1-y_axis_scaler)
manda_y_axis_min
```

Convert MICP year column to numeric

```{r}
df7$year = as.numeric(as.character(df7$year)) 
df7
```

Summarise Lamu data

```{r}
summary(df8)
```

Calculate Lamu data min and max values and store as a vector

```{r}
lamu_range <- range(df8$Total_Mangroves_Hectares)
lamu_range
```

Define the Lamu line graph Y axis limit as 3% above the Lamu data Max value.

```{r}
lamu_y_axis_max <- lamu_range[2] * (1+y_axis_scaler)
lamu_y_axis_max
```

Define the Lamu line graph Y axis limit as 3% below the Lamu data Min value.

```{r}
lamu_y_axis_min <- lamu_range[1] * (1-y_axis_scaler)
lamu_y_axis_min
```

Convert Lamu year column to numeric.

```{r}
df8$year = as.numeric(as.character(df8$year)) 
df8
```

Create line and bar plots showing mangrove coverage over time in Lamu County and the MICP

```{r}
p1 <- ggplot(data=df8, aes(x=year, y=Total_Mangroves_Hectares, group=1)) +
    geom_line() +
    geom_point() +
  theme_fancy() +
  ylim(lamu_y_axis_min, lamu_y_axis_max) +
  ggtitle("Lamu County") +
  xlab("Year") +
  ylab("Mangroves in Ha")

p2 <- ggplot(data=df7, aes(x=year, y=Total_Mangroves_Hectares, group=1)) +
    geom_line() +
    geom_point() +
  theme_fancy() +
  ylim(manda_y_axis_min, manda_y_axis_max) +
  ggtitle("MICP") +
  xlab("Year") +
  ylab("Mangroves in Ha")

p3 <- ggplot(data=df8, aes(x=year, y=Total_Mangroves_Hectares)) +
    geom_bar(stat="identity") +
  theme_fancy() +
  ggtitle("Lamu County") +
  xlab("Year") +
  ylab("Mangroves in Ha")

p4 <- ggplot(data=df7, aes(x=year, y=Total_Mangroves_Hectares)) +
    geom_bar(stat="identity") +
  theme_fancy() +
  ggtitle("MICP") +
  xlab("Year") +
  ylab("Mangroves in Ha")

fig2 <- p1 + p2 + p3 + p4 + plot_annotation(tag_levels = 'a') + 
  plot_annotation(title = 'Lamu County and MICP mangrove cover 1996 to 2020', theme = theme(plot.title = element_text(size = 12, face="bold"))) 

fig2 
```

Save the plots

```{r}
filename = "Lamu County vs MICP cover change 1996-2020"

ggsave(
  fig2,
  filename = paste0("Plots/", filename, ".png"),
  width = 23,
  height = 17,
  units = "cm"
)

ggsave(
  fig2,
  filename = paste0("Plots/", filename, ".pdf"),
  width = 23,
  height = 17,
  units = "cm"
)
```
