---
title: "Amy Shaw Dissertation Code Script"
output: html_notebook
---

Load packages 

```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(patchwork)
```

```{r}
library(data.table)
library(scales)
```

Setting Potting Theme 

```{r}
theme_fancy <- function() {
  theme_bw() +
    theme(
      text = element_text(family = "Helvetica"),
      axis.text = element_text(size = 8, color = "black"),
      axis.title = element_text(size = 10, color = "black"),
      axis.line.x = element_line(size = 0.3, color = "black"),
      axis.line.y = element_line(size = 0.3, color = "black"),
      axis.ticks = element_line(size = 0.3, color = "black"),
      panel.border = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank(),
      panel.grid.minor.y = element_blank(),
      panel.grid.major.y = element_blank(),
      plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), units = , "cm"),
      plot.title = element_text(
        size = 10,
        vjust = 1,
        hjust = 0.5,
        color = "black"
      ),
      legend.text = element_text(size = 9, color = "black"),
      legend.title = element_text(size = 9, color = "black"),
      legend.position = c(0.9, 0.9),
      legend.key.size = unit(0.7, "line"),
      legend.background = element_rect(
        color = "black",
        fill = "transparent",
        size = 2,
        linetype = "blank"
      )
    )
}
```

Import all Lamu County mangrove cover data sets 

Import Lamu County 1996 Mangrove Data 

```{r}
Lamu1996Data <- read_csv("Data/Lamu1996Data.csv")
Lamu1996Data
```
Rename 1996 column to mangroves 

```{r}
names(Lamu1996Data)[names(Lamu1996Data) == '1996'] <- 'Mangroves'
Lamu1996Data
```
Create a 1996 year column 

```{r}
Lamu1996Data <- cbind(Lamu1996Data, year="1996")
Lamu1996Data
```
Drop columns PXLVAL and clipped1996data as neither is needed 

```{r}
Lamu1996Data = subset(Lamu1996Data,select = -c(PXLVAL, clipped1996data))
Lamu1996Data
```
Import Lamu County 2007 Mangrove Data 

```{r}
Lamu2007Data <- read_csv("Data/Lamu2007Data.csv")
Lamu2007Data
```
Rename 2007 year to mangroves 

```{r}
names(Lamu2007Data)[names(Lamu2007Data) == '2007'] <- 'Mangroves'
Lamu2007Data
```

Create a 2007 year column 

```{r}
Lamu2007Data <- cbind(Lamu2007Data, year="2007")
Lamu2007Data
```

Drop columns PXLVAL and clipped2007data as neither is needed 

```{r}
Lamu2007Data = subset(Lamu2007Data,select = -c(PXLVAL, clipped2007data))
Lamu2007Data
```
Import Lamu County 2008 Mangrove Data 

```{r}
Lamu2008Data <- read_csv("Data/Lamu2008Data.csv")
Lamu2008Data
```

Rename 2008 column to mangroves 

```{r}
names(Lamu2008Data)[names(Lamu2008Data) == '2008'] <- 'Mangroves'
Lamu2008Data
```
Create a 2008 year column 

```{r}
Lamu2008Data <- cbind(Lamu2008Data, year="2008")
Lamu2008Data
```

Drop columns PXLVAL and clipped2008data as neither is needed 

```{r}
Lamu2008Data = subset(Lamu2008Data,select = -c(PXLVAL, clipped2008data))
Lamu2008Data
```

Import Lamu County 2009 Mangrove Data 

```{r}
Lamu2009Data <- read_csv("Data/Lamu2009Data.csv")
Lamu2009Data
```
Rename 2009 column to mangroves 

```{r}
names(Lamu2009Data)[names(Lamu2009Data) == '2009'] <- 'Mangroves'
Lamu2009Data
```

Create a 2009 year column 

```{r}
Lamu2009Data <- cbind(Lamu2009Data, year="2009")
Lamu2009Data
```

Drop columns PXLVAL and clipped2009data as neither is needed 

```{r}
Lamu2009Data = subset(Lamu2009Data,select = -c(PXLVAL, clipped2009data))
Lamu2009Data
```

Import Lamu County 2010 Mangrove Data 

```{r}
Lamu2010Data <- read_csv("Data/Lamu2010Data.csv")
Lamu2010Data
```

Rename 2010 column to mangroves 

```{r}
names(Lamu2010Data)[names(Lamu2010Data) == '2010'] <- 'Mangroves'
Lamu2010Data
```

Create a 2010 year column 

```{r}
Lamu2010Data <- cbind(Lamu2010Data, year="2010")
Lamu2010Data
```

Drop columns PXLVAL and clipped2010data as neither is needed 

```{r}
Lamu2010Data = subset(Lamu2010Data,select = -c(PXLVAL, clipped2010data))
Lamu2010Data
```

Import Lamu County 2015 Mangrove Data 

```{r}
Lamu2015Data <- read_csv("Data/Lamu2015Data.csv")
Lamu2015Data
```

Rename 2015 column to mangroves 

```{r}
names(Lamu2015Data)[names(Lamu2015Data) == '2015'] <- 'Mangroves'
Lamu2015Data
```

Create a 2015 year column 

```{r}
Lamu2015Data <- cbind(Lamu2015Data, year="2015")
Lamu2015Data
```

Drop columns PXLVAL and clipped2015data as neither is needed 

```{r}
Lamu2015Data = subset(Lamu2015Data,select = -c(PXLVAL, clipped2015data))
Lamu2015Data
```

Import Lamu County 2016 Mangrove Data 

```{r}
Lamu2016Data <- read_csv("Data/Lamu2016Data.csv")
Lamu2016Data
```

Rename 2016 column to mangroves 

```{r}
names(Lamu2016Data)[names(Lamu2016Data) == '2016'] <- 'Mangroves'
Lamu2016Data
```

Create a 2016 year column 

```{r}
Lamu2016Data <- cbind(Lamu2016Data, year="2016")
Lamu2016Data
```

Drop columns PXLVAL and clipped2016data as neither is needed 

```{r}
Lamu2016Data = subset(Lamu2016Data,select = -c(PXLVAL, clipped2016data))
Lamu2016Data
```

Import Lamu County 2017 Mangrove Data 

```{r}
Lamu2017Data <- read_csv("Data/Lamu2017Data.csv")
Lamu2017Data
```
Rename 2017 column to Mangroves 

```{r}
names(Lamu2017Data)[names(Lamu2017Data) == '2017'] <- 'Mangroves'
Lamu2017Data
```

Create a 2017 year column 

```{r}
Lamu2017Data <- cbind(Lamu2017Data, year="2017")
Lamu2017Data
```

Drop columns PXLVAL and clipped2017data as neither is needed 

```{r}
Lamu2017Data = subset(Lamu2017Data,select = -c(PXLVAL, clipped2017data))
Lamu2017Data
```

Import Lamu County 2018 Mangrove Data 

```{r}
Lamu2018Data <- read_csv("Data/Lamu2018Data.csv")
Lamu2018Data
```
Rename 2018 column to Mangroves 

```{r}
names(Lamu2018Data)[names(Lamu2018Data) == '2018'] <- 'Mangroves'
Lamu2018Data
```

Create a 2018 year column 

```{r}
Lamu2018Data <- cbind(Lamu2018Data, year="2018")
Lamu2018Data
```
Drop PXLVAL column as it is not needed 

```{r}
Lamu2018Data = subset(Lamu2018Data,select = -c(PXLVAL))
Lamu2018Data
```

Import Lamu County 2019 Mangrove Data 

```{r}
Lamu2019Data <- read_csv("Data/Lamu2019Data.csv")
Lamu2019Data
```

Rename 2019 column to Mangroves 

```{r}
names(Lamu2019Data)[names(Lamu2019Data) == '2019'] <- 'Mangroves'
Lamu2019Data
```
Create a 2019 year column 

```{r}
Lamu2019Data <- cbind(Lamu2019Data, year="2019")
Lamu2019Data
```

Drop columns PXLVAL and clipped2019data as neither is needed 

```{r}
Lamu2019Data = subset(Lamu2019Data,select = -c(PXLVAL, clipped2019data))
Lamu2019Data
```

Import Lamu County 2020 Mangrove Data 

```{r}
Lamu2020Data <- read_csv("Data/Lamu2020Data.csv")
Lamu2020Data
```

Rename 2020 column to Mangroves 

```{r}
names(Lamu2020Data)[names(Lamu2020Data) == '2020'] <- 'Mangroves'
Lamu2020Data
```
Create a 2020 year column 

```{r}
Lamu2020Data <- cbind(Lamu2020Data, year="2020")
Lamu2020Data
```
Drop columns PXLVAL and clipped2020data as neither is needed 

```{r}
Lamu2020Data = subset(Lamu2020Data,select = -c(PXLVAL, clipped2020data))
Lamu2020Data
```

Combine all Lamu County Mangrove Datasets by year 

```{r}
df1 <- bind_rows(Lamu1996Data, Lamu2007Data, Lamu2008Data, Lamu2009Data, Lamu2010Data, Lamu2015Data, Lamu2016Data, Lamu2017Data, Lamu2018Data, Lamu2019Data, Lamu2020Data)
df1
```

Check unique values to make sure each year has been included 

```{r}
unique(df1$year)
```


Group mangroves by year

```{r}
agg_tbl <- df1 %>% group_by(year) %>% summarise(Total_Mangroves=sum(Mangroves),.groups = 'drop')
agg_tbl
```


Convert to a new dataframe 

```{r}
df2 <- agg_tbl %>% as.data.frame()
df2
```
Convert Mangrove cover to hectares

```{r}
df2$Total_Mangroves_Hectares <- df2$Total_Mangroves / 10000
df2
```

Drop Total_Mangroves columns as unnesessary 

```{r}
df2 = subset(df2,select = -c(Total_Mangroves))
df2
```

Duplicate dataset 

```{r}
df3 <- df2
df3
```




